\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-03-02 jasa/paper-jasa.tex
Compare with true contours

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig5.pdf}
    \caption{Parameter inference from parameterized approximated likelihood ratios.
             The constructed objective is minimized with Bayesian optimization.
             Red dots correspond to sampled candidate pairs $(A,B)$.
             The blue dot corresponds to the minimum found after $50$ iterations. Nominal values are $A=1$ and $B=-1$.}
    \label{fig:5}
\end{figure}

As previously, we make use of Eqn.~\ref{eq:mle_withs} for parameter inference
with approximated likelihood ratios and fix the alternate to $\theta_1:=(A=0,
B=0)$. Following recommendations from Section~\ref{sec:param-clf} to reduce
computational requirements, we train a single parameterized classifier
$s(\mathbf{x};\theta:=(A,B),\theta_1)$; in this case, a 2-layer neural network.
Since the generative model is not expensive, the classifier output is calibrated on-the-fly
with isotonic regression for every candidate parameter pair $\theta:=(A,B)$.
Minimizing the mean negative log of the constructed objective with Bayesian
optimization~\citep{brochu2010tutorial} eventually leads to the estimated
posterior mean and variance shown in Figure~\ref{fig:5}. The objective is minimized after $50$ iterations
at $(\hat A=1.00,\hat B=-1.15)$. Again, repeated experiments (omitted here) confirm that
the proposed procedure yields an unbiased maximum likelihood estimator.

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[height=12.5em]{figures/fig5a.pdf}
        \caption{True mean negative log-ratio}
        \label{fig:5a}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[height=12.5em]{figures/fig5b.pdf}
        \caption{Estimated mean negative log-ratio}
        \label{fig:5b}
    \end{subfigure}
    \caption{Inference from parameterized approximated likelihood ratios.
             (\ref{fig:5a}) True mean negative log-ratio for the observed data ${\cal D}$. The red dot corresponds to the nominal values $A=1, B=-1$, while the green dot is the maximum likelihood estimator $\hat A=1.006, \hat B=-1.012$.
             (\ref{fig:5a}) Estimated mean negative log-ratio, as approximated from the constructed objective by the gaussian process within the Bayesian optimization process. The blue dot is the estimated maximum likelihood estimator $\hat A=0.956, \hat B=-0.869$ while the white dots correspond to the points sampled during optimization.}
    \label{fig:5}
\end{figure}

As previously, we make use of Eqn.~\ref{eq:mle_withs} for parameter inference
with approximated likelihood ratios and fix the alternate to $\theta_1:=(A=0,
B=0)$. Following recommendations from Section~\ref{sec:param-clf} to reduce
computational requirements, we train a single parameterized classifier
$s(\mathbf{x};\theta:=(A,B),\theta_1)$; in this case, a 2-layer neural network.
Since the generative model is not expensive, the classifier output is calibrated on-the-fly
with isotonic regression for every candidate parameter pair $\theta:=(A,B)$.
Minimizing the mean negative log of the constructed ratio with Bayesian
optimization~\citep{brochu2010tutorial} eventually leads to the estimated
posterior mean shown in Figure~\ref{fig:5b}, which is close to the true objective illustrated in Figure~\ref{fig:5a}. After $50$ iterations,
the estimated minimizer is found at $(\hat A=0.956, \hat B=-0.869$). 
Again, repeated experiments (omitted here) confirm that
the proposed procedure yields an unbiased maximum likelihood estimator.
